Title

### 2013-01-25 inc/extension/external_forces/external_forces.tex
began work on modeling accelerator, its in the gun folder now, depending on overlap might move to external_forces
small fixes

\subsection{Constant External Forces}

@@

A magnetic lens may be modeled using one linear force contribution.
Unfortunately, it is not practical to write an analytic form of the magnitude of this term; the field distribution is very complicated to describe \cite{montgomery_some_1961} and the ``lensing'' action is actually a compound force (first rotating the beam, then lensing, see Section \ref{sec:mag_lens}).
We have found that in practice, characterizing a specific magnetic lens ($M_{\smallT}(I)$ where $I$ is the current in the magnetic lens) is much easier than attempting to find a generic functional form.

>>>>

\subsection{Constant External Forces} \label{sec:const_force}

@@

A magnetic lens may be modeled using one linear force contribution.
Unfortunately, it is not practical to write an analytic form of the magnitude of this term; the field distribution is very complicated to describe \cite{montgomery_some_1961} and the ``lensing'' action is actually a compound force (first rotating the beam, then lensing).
We have found that in practice, characterizing a specific magnetic lens ($M_{\smallT}(I)$ where $I$ is the current in the magnetic lens) is much easier than attempting to find a generic functional form.
Further discussion of magnetic lenses can be found in Section \ref{sec:mag_lens}.

### 2013-01-25 inc/extension/initial_conditions/initial_conditions.tex
fix equation, add longitudinal model datas and plot/fitting
small fixes

%v0 dominated
In the short pulse limit, where the acceleration in the DC gun field over the incident laser pulse duration can be neglected, the initial electron bunch properties are determined primarily by the photoemission physics.
%TODO describe new model
Careful analysis of the electron generation using the longitudinal $ v^{3} $ photoemission velocity distribution (Appendix \ref{sec:step_model}) and iterative time steps through the incident laser pulse reveals that, although the spatial electron bunch distribution is slightly skewed with respect to the symmetric incident laser pulse, its initial variance $ \sqrt{ \sigma_{ z } ( 0 ) } $ (or width) is nearly equal to that of the laser pulse of the normalization by the velocity ratio $ v_{ 0 }/c $; in other words,
\begin{equation} \label{eq:initial_sigma_z}
\sqrt{ \sigma_{ z } ( 0 ) } = v_{ 0 } \Delta t_{L} = \frac{ v_{ 0 } \tau }{ \sqrt{ 2 } } \, \text{.}
\end{equation}
Not unexpectedly, the analysis also indicates that the initial electron bunch has a velocity chirp.
%TODO description again
Its value is only roughly 6\% of $ v_{ 0 }/\sqrt{ \sigma_{z} ( 0 ) } $ since the photoemission generates the $ v^{ 3 } $ velocity distribution throughout the laser pulse; thus 
\begin{equation}
\gamma_{ z } ( 0 ) = m \sigma_{ z } ( 0 ) \frac{ d v }{ d z } \approx 0.06 m v_{ 0 } \sqrt{ \sigma_{ z } ( 0 ) } \, ,
\end{equation}
in this regime.
Additionally the iterative time-step analysis clearly shows that the local longitudinal momentum variance $ \eta_{ z } $ is not constant over the inital photo-generated electron bunch.
In fact, $ \sqrt{ \eta_{ z } ( 0 ) } $ varies by almost an order of magnitude over the $ 1/e^{2} $ maximum full-width of the electron bunch with the narrowest momentum distribution at the front of the bunch where only the faster electrons with velocity near $ v_{ 0 } $ initially reside.
Unfortunately, the mean-field theory of Michalik and Sipe \cite{michalik_analytic_2006} is not equipped to handle such a variation as it assumes a constant $ \eta_{ z } $ over the electron bunch.
Consequently, we will assume that $ \eta_{ z } $ is a constant over the bunch with a value given by $ \eta_{\smallT } ( 0 ) \cong 3.85 \eta{ z } ( 0 ) $ (see Appendix \ref{sec:step_model}): indeed in this short pulse regime, one can show that over the central $ \sim 75 \% $ of the electrons in the inital photo-generated bunch the variation in $ \sqrt{ \eta_{ z } ( 0 ) } $ is only about $ \pm 25 \% $.

These initial conditions at $t=0$ for an incident Gaussian laser pulse of the form given in \ref{eq:laser_form}, will be used for the remainder of this paper.
\begin{subequations} \label{eq:summary}
  \begin{gather}
    \sigma_{ \smallT } ( 0 ) = \frac{ w^{ 2 } }{ 2 } \\
    \sigma_{ z } ( 0 ) = \frac{ ( v_{ 0 } \tau )^{ 2 } }{ 2 } + \left ( \frac{ e E_{ DC } \tau^{ 2 } }{ 4 m } \right )^{ 2 } \\
    \gamma_{ \smallT } ( 0 ) = 0 \\
    \gamma_{ z } ( 0 ) = \sqrt{ \sigma_{ z } ( 0 ) } \left ( 0.06 m v_{ 0 } + \frac{ e E_{DC} \tau }{ \sqrt{ 2 } } \right ) \\
    \eta_{ \smallT } ( 0 ) = \frac{ m \epsilon_{ F } ( \hbar \omega - \Phi ) }{ 3 ( \hbar \omega + \epsilon_{ F } ) } \\
    \eta_{ z } ( 0 ) = \frac{ \eta_{ \smallT } ( 0 ) }{ 3.85 }
  \end{gather}
\end{subequations}

>>>>

%v0 dominated
In the short pulse limit, where the acceleration in the DC gun field over the incident laser pulse duration can be neglected, the initial electron bunch properties are determined primarily by the photoemission physics.
%TODO describe new model
Careful analysis of the electron generation using the longitudinal $ v^{3} $ photoemission velocity distribution %TODO reference bin model
and iterative time steps through the incident laser pulse reveals that, although the spatial electron bunch distribution is slightly skewed with respect to the symmetric incident laser pulse, its initial variance $ \sqrt{ \sigma_{ z } ( 0 ) } $ (or width) is nearly equal to that of the laser pulse of the normalization by the velocity ratio $ v_{ 0 }/c $; in other words,
\begin{equation} \label{eq:initial_sigma_z}
\sqrt{ \sigma_{ z } ( 0 ) } = v_{ 0 } \Delta t_{L} = \frac{ v_{ 0 } \tau }{ \sqrt{ 2 } } \, \text{.}
\end{equation}
Not unexpectedly, the analysis also indicates that the initial electron bunch has a velocity chirp.
%TODO description again
Its value is only roughly 6\% of $ v_{ 0 }/\sqrt{ \sigma_{z} ( 0 ) } $ since the photoemission generates the $ v^{ 3 } $ velocity distribution throughout the laser pulse; thus 
\begin{equation}
\gamma_{ z } ( 0 ) = m \sigma_{ z } ( 0 ) \frac{ d v }{ d z } \approx 0.06 m v_{ 0 } \sqrt{ \sigma_{ z } ( 0 ) } \, ,
\end{equation}
in this regime.
Additionally the iterative time-step analysis clearly shows that the local longitudinal momentum variance $ \eta_{ z } $ is not constant over the inital photo-generated electron bunch.
In fact, $ \sqrt{ \eta_{ z } ( 0 ) } $ varies by almost an order of magnitude over the $ 1/e^{2} $ maximum full-width of the electron bunch with the narrowest momentum distribution at the front of the bunch where only the faster electrons with velocity near $ v_{ 0 } $ initially reside.
Unfortunately, the mean-field theory of Michalik and Sipe \cite{michalik_analytic_2006} is not equipped to handle such a variation as it assumes a constant $ \eta_{ z } $ over the electron bunch.
Consequently, we will assume that $ \eta_{ z } $ is a constant over the bunch with a value given by $ \eta_{\smallT } ( 0 ) \cong 3.85 \eta{ z } ( 0 ) $: %TODO reference bin model
indeed in this short pulse regime, one can show that over the central $ \sim 75 \% $ of the electrons in the inital photo-generated bunch the variation in $ \sqrt{ \eta_{ z } ( 0 ) } $ is only about $ \pm 25 \% $.

These initial conditions at $t=0$ for an incident Gaussian laser pulse of the form given in \ref{eq:laser_form}, will be used for the remainder of this paper.
\begin{subequations} \label{eq:summary}
  \begin{gather}
    \sigma_{ \smallT } ( 0 ) = \frac{ w^{ 2 } }{ 2 } \\
    \sigma_{ z } ( 0 ) = \frac{ ( v_{ 0 } \tau )^{ 2 } }{ 2 } + \left ( \frac{ e E_{ DC } \tau^{ 2 } }{ 4 m } \right )^{ 2 } \\
    \gamma_{ \smallT } ( 0 ) = 0 \\
    \gamma_{ z } ( 0 ) = \sqrt{ \sigma_{ z } ( 0 ) } \left ( 0.06 m v_{ 0 } + \frac{ e E_{DC} \tau }{ \sqrt{ 2 } } \right ) \\
    \eta_{ \smallT } ( 0 ) = \frac{ m }{ 3 } ( \hbar \omega - \Phi ) \\
    \eta_{ z } ( 0 ) = \frac{ \eta_{ \smallT } ( 0 ) }{ 3.85 }
  \end{gather}
\end{subequations}
